### 2019-11-28 boek.tex
add back dyngen submodule, apply small changes
Reordered chapters.

\PassOptionsToPackage{table}{xcolor}
\documentclass[10pt]{book}

@@

% adjust margins (should be done before importing fancyhdr!)
\usepackage[paperheight=24cm,paperwidth=16cm,margin=2.5cm,a4paper]{geometry} %lmargin=2.5cm,rmargin=4cm,tmargin=3cm,bmargin=3cm

@@

\newlength{\thumbwidth}
\setlength{\thumbwidth}{1.5cm}

@@

\renderalltrue

@@

% thesis obligatory content: 
% * an abstract in Dutch
% * a list of abbreviations
% * one uniform (compiling) reference list
% * a resume or Curriculum Vitae of the candidate
% * an introductory chapter and additional linking texts between chapters (papers) if the dissertation consists of a compilation of papers
% * acknowledgements of financing institutions
% * apply for an ISBN number for your thesis. This takes 1-2 days.

@@

%{\large \textbf{Abstract}}
\begin{quote}
	%Recent developments in single-cell transcriptomics have opened new opportunities for studying dynamic processes in a high-throughput and unbiased manner. Starting from a mixture of cells in different stages of a developmental process, unsupervised trajectory inference algorithms aim to automatically reconstruct the underlying developmental path that cells are following. In this review, we break down the strategies used by this novel class of methods, and organize their components into a common framework, highlighting several practical advantages and disadvantages of the individual methods. We also give an overview of new insights these methods have already provided regarding the wiring and gene regulation of cell differentiation. As the trajectory inference field is still in its infancy, we propose several future developments which will ultimately lead to a global and data-driven way of studying immune cell differentiation.
\end{quote}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%        CH2: DYNGEN        %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 1: Benchmarking with \textit{in silico} single cells} 
\chaptermark{Paper 1: Benchmarking with \textit{in silico} single cells.}
\label{chap:dyngen}

@@

\vfill
{\large \textbf{Author contributions}}
\begin{quote}
	$\bullet$ \textbf{R.C.} and W.S. designed the study.\\
	$\bullet$ \textbf{R.C.} and W.S. performed the experiments and analysed the data.\\
	$\bullet$ \textbf{R.C.} and W.S. implemented software packages.\\
	$\bullet$ \textbf{R.C.} wrote the original manuscript.\\
	$\bullet$ \textbf{R.C.} and W.S. reviewed and edited the manuscript. \\
	$\bullet$ Y.S. supervised the project.
\end{quote}

@@

\ifrenderall
\newpage
\graphicspath{{./ch2_dyngen/}}
\include{ch2_dyngen/content}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%     CH3: DYNBENCHMARK     %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 2: A comparison of single-cell trajectory inference methods} 
\chaptermark{Paper 2: A comparison of single-cell trajectory inference methods.}
\label{chap:dynbenchmark}

@@

\ifrenderall
\newpage
\graphicspath{{./ch3_dynbenchmark/}}
\include{ch3_dynbenchmark/content}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH4: DYNO         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 3: A toolkit for inferring and interpreting trajectories} 
\chaptermark{Paper 3: A toolkit for inferring and interpreting trajectories.} % short title
\label{chap:dyno}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH5: SCORPIUS       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 4: Fast, accurate, and robust single-cell pseudotime} 
\chaptermark{Paper 4: Fast, accurate, and robust single-cell pseudotime.} % short title
\label{chap:scorpius}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH6: BRED         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 5: Inferring single cell regulatory networks} 
\chaptermark{Paper 5: Inferring single cell regulatory networks.} % short title
\label{chap:bred}

@@

\ifrenderall
\newpage
\graphicspath{{./ch6_bred/}}
\include{ch6_bred/content}
\fi 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH7: INCGRAPH       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 6: Optimising regulatory networks} 
\chaptermark{Paper 6: Optimising regulatory networks.} % short title
\label{chap:incgraph}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%   CH8: Self-assessment    %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 7: Self-assessment in trajectory inference} 
\chaptermark{Paper 7: Self-assessment in trajectory inference.} % short title
\label{chap:selfassessment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH9: Guidelines    %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 8: Essential guidelines for computational method benchmarking} 
\chaptermark{Paper 8: Essential guidelines for computational method benchmarking.} % short title
\label{chap:guidelines}

>>>>

\PassOptionsToPackage{table}{xcolor}
\documentclass[8pt]{book}

@@

\usepackage[paperheight=24cm,paperwidth=17cm,margin=1.5cm]{geometry}

\usepackage[
	% set width and height to a4 width and height + 6mm
	%width=16truecm, height=24truecm,
	a4,
	% use any combination of these options to add different cut markings
	cam, axes, frame, cross,
	% set the type of TeX renderer you use
	pdftex,
	% center the contents
	center
]{crop}

% adjust margins (should be done before importing fancyhdr!) %lmargin=2.5cm,rmargin=4cm,tmargin=3cm,bmargin=3cm

@@

\newlength{\thumbwidth}
\setlength{\thumbwidth}{1cm}

@@

%\renderalltrue

@@

@@

%{\large \textbf{Abstract}}
%\begin{quote}
	%Recent developments in single-cell transcriptomics have opened new opportunities for studying dynamic processes in a high-throughput and unbiased manner. Starting from a mixture of cells in different stages of a developmental process, unsupervised trajectory inference algorithms aim to automatically reconstruct the underlying developmental path that cells are following. In this review, we break down the strategies used by this novel class of methods, and organize their components into a common framework, highlighting several practical advantages and disadvantages of the individual methods. We also give an overview of new insights these methods have already provided regarding the wiring and gene regulation of cell differentiation. As the trajectory inference field is still in its infancy, we propose several future developments which will ultimately lead to a global and data-driven way of studying immune cell differentiation.
%\end{quote}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%        CH2: DYNGEN        %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{dyngen: Benchmarking with \textit{in silico} single cells} 
\chaptermark{dyngen: Benchmarking with \textit{in silico} single cells.}
\label{chap:dyngen}

@@

\vfill
{\large \textbf{Publication status}}
\begin{quote}
	Manuscript in preparation. \\
	\textbf{Cannoodt R}$^*$, Saelens W$^*$, Deconinck L, and Saeys Y.  \\
	{\footnotesize $^*$ Equal contribution}
\end{quote}

\vfill
{\large \textbf{Author contributions}}
\begin{quote}
	$\bullet$ \textbf{R.C.} and W.S. designed the study.\\
	$\bullet$ \textbf{R.C.}, W.S., and L.D. performed the experiments and analysed the data.\\
	$\bullet$ \textbf{R.C.} and W.S. implemented software packages.\\
	$\bullet$ \textbf{R.C.} wrote the original manuscript.\\
	$\bullet$ \textbf{R.C.}, W.S., L.D., and Y.S. reviewed and edited the manuscript. \\
	$\bullet$ Y.S. supervised the project.
\end{quote}

@@

\ifrenderall
\newpage
\graphicspath{{./ch2_dyngen/}}
\include{ch2_dyngen/content}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%     CH3: DYNBENCHMARK     %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{dynbenchmark: A comparison of single-cell trajectory inference methods} 
\chaptermark{dynbenchmark: A comparison of single-cell trajectory inference methods.}
\label{chap:dynbenchmark}

@@

\ifrenderall
\newpage
\graphicspath{{./ch3_dynbenchmark/}}
\include{ch3_dynbenchmark/content}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%   CH4: Self-assessment    %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Self-assessment in trajectory inference} 
\chaptermark{Self-assessment in trajectory inference.} % short title
\label{chap:selfassessment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH5: SCORPIUS       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{SCORPIUS: Fast, accurate, and robust single-cell pseudotime} 
\chaptermark{SCORPIUS: Fast, accurate, and robust single-cell pseudotime.} % short title
\label{chap:scorpius}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH6: DYNO         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{dyno: A toolkit for inferring and interpreting trajectories} 
\chaptermark{dyno: A toolkit for inferring and interpreting trajectories.} % short title
\label{chap:dyno}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH7: BRED         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{bred: Inferring single cell regulatory networks} 
\chaptermark{bred: Inferring single cell regulatory networks.} % short title
\label{chap:bred}

@@

\ifrenderall
\newpage
\graphicspath{{./ch6_bred/}}
\include{ch6_bred/content}
\fi 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH8: INCGRAPH       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{incgraph: Optimising regulatory networks} 
\chaptermark{incgraph: Optimising regulatory networks.} % short title
\label{chap:incgraph}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH9: Guidelines    %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Essential guidelines for computational method benchmarking} 
\chaptermark{Essential guidelines for computational method benchmarking.} % short title
\label{chap:guidelines}
